02_limma_vomm_pit

### 2019-03-19 scripts/02_limma_pit.Rmd
add males

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../results/00_colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
head(colData)
geneinfo <- read.csv("../results/00_geneinfo.csv", row.names = 1)
```

@@

@@

# specify contrasts and make MA plots (currently only a subset)

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         FP_CB = female.pituitary.control - female.pituitary.bldg,
	         FP_BL = female.pituitary.bldg - female.pituitary.lay,
	         FP_Li3 = female.pituitary.lay - female.pituitary.inc.d3,
	         FP_i39 = female.pituitary.inc.d3 - female.pituitary.inc.d9,
	         FP_i917 = female.pituitary.inc.d9 - female.pituitary.inc.d17,
	         FP_i17H = female.pituitary.inc.d17 - female.pituitary.hatch,
	         FP_H5 = female.pituitary.hatch -  female.pituitary.n5,
	         FP_n59 = female.pituitary.n5 - female.pituitary.n9,
	         FP_n9C = female.pituitary.n9 - female.pituitary.control,
levels=parentaldesign)

cont <- "FP_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_CB', frame.plot=F)

@@

cont <- "FP_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_n9C', frame.plot=F)
```

>>>>

```{r read}
# import "colData" which contains sample information and "countData" which contains read counts
colData <- read.csv("../results/00_colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
geneinfo <- read.csv("../results/00_geneinfo.csv", row.names = 1)
```

@@

For color coding, I used this tutorial for guidance <https://combine-australia.github.io/RNAseq-R/06-rnaseq-day1.html>.

@@

# specify contrasts and make MA plots

@@

# subset of conrasts - sex specific comparing hatch to lay
my.contrasts <- makeContrasts(
	         FP_CB = female.pituitary.control - female.pituitary.bldg,
	         FP_BL = female.pituitary.bldg - female.pituitary.lay,
	         FP_Li3 = female.pituitary.lay - female.pituitary.inc.d3,
	         FP_i39 = female.pituitary.inc.d3 - female.pituitary.inc.d9,
	         FP_i917 = female.pituitary.inc.d9 - female.pituitary.inc.d17,
	         FP_i17H = female.pituitary.inc.d17 - female.pituitary.hatch,
	         FP_H5 = female.pituitary.hatch -  female.pituitary.n5,
	         FP_n59 = female.pituitary.n5 - female.pituitary.n9,
	         FP_n9C = female.pituitary.n9 - female.pituitary.control,

	         MP_CB = male.pituitary.control - male.pituitary.bldg,
	         MP_BL = male.pituitary.bldg - male.pituitary.lay,
	         MP_Li3 = male.pituitary.lay - male.pituitary.inc.d3,
	         MP_i39 = male.pituitary.inc.d3 - male.pituitary.inc.d9,
	         MP_i917 = male.pituitary.inc.d9 - male.pituitary.inc.d17,
	         MP_i17H = male.pituitary.inc.d17 - male.pituitary.hatch,
	         MP_H5 = male.pituitary.hatch -  male.pituitary.n5,
	         MP_n59 = male.pituitary.n5 - male.pituitary.n9,
	         MP_n9C = male.pituitary.n9 - male.pituitary.control,
levels=parentaldesign)

# female comparisons
cont <- "FP_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_CB', frame.plot=F)

@@

cont <- "FP_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='FP_n9C', frame.plot=F)

## male comparisons

cont <- "MP_CB"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_CB', frame.plot=F)

cont <- "MP_BL"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_BL', frame.plot=F)

cont <- "MP_Li3"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_Li3', frame.plot=F)

cont <- "MP_i39"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i39', frame.plot=F)

cont <- "MP_i917"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i917', frame.plot=F)

cont <- "MP_i17H"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_i17H', frame.plot=F)

cont <- "MP_H5"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_H5', frame.plot=F)

cont <- "MP_n59"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_n59', frame.plot=F)

cont <- "MP_n9C"
summary(decideTestsDGE(
	glmTreat(fit, contrast=my.contrasts[,cont], lfc = 1), 
	adjust.method="fdr", p.value=0.01))
kable(topTags(glmTreat(fit, contrast=my.contrasts[,cont]), n=5), digits=2, lfc = 1)
plotMD(glmTreat(fit, contrast=my.contrasts[,cont], lfc=1), main='MP_n9C', frame.plot=F)
